GPU-friendly Stroke Expansion

### 2024-06-14 paper.tex

The distance between a circular arc segment of length $s$ and its chord, with angle between arc and chord of $\theta$ (see Figure~\ref{fig:arc_chord}), is exactly $(1-\cos \theta)\frac{s}{2\theta}$. The curvature is $\kappa = \frac{2\theta}{s}$ (equivalently, $\theta = \frac{\kappa s}{2}$), and this remains constant even as the arc is subdivided. Rewriting, $d = (1-\cos\frac{\kappa s}{2})\frac{1}{\kappa}$. From this, we can derive a precise, invertible error metric. Subdividing the arc in to $n$ segments, the distance error for each segment is $\frac{1}{\kappa}(1-\cos \frac{\kappa s}{2n})$. Solving for $n$, we get:

@@

The subdivision density integral (Section~\ref{subsection:subdiv-density-int}) is fairly straightforward to compute in the forward direction, but not invertible using a straightforward closed-form equation. Numerical techniques are possible, but require multiple iterations to achieve sufficient accuracy, so are slower. In this subsection, we present a straightforward and accurate approximation, constructed piecewise from easily invertible functions. If higher flattening quality is desired at the expense of slower computation, this approximation can be used to determine a good initial value for numeric techniques; two iterations of Newton solving are enough to refine this guess to within 32-bit floating point accuracy.

The approximation is given as follows:

@@

A typical pattern for converting from one curve type to another is \emph{adaptive subdivision.} An approximate curve is found in the parameter space of the target curve family. The error of the approximation is measured. If the error exceeds the specified tolerance, the curve is subdivided (typically at $t = 0.5$), otherwise the approximation is accepted. Subdivisions are also indicated at special points; for example, since quadratic Béziers cannot represent inflection points, and geometric Hermite interpolation is numerically unstable if the input curve is not convex, lowering to quadratic Béziers also requires calculation of inflection points and subdividing there. A good example of this pattern is \citet{Nehab2020}. One advantage of Euler spirals over quadratic Béziers is that they can represent inflection points just fine, so it is not necessary to compute those for additional subdivision.

>>>>

The distance between a circular arc segment of length $s$ and its chord, with angle between arc and chord of $\theta$ (see Figure~\ref{fig:arc_chord}), is exactly $(1-\cos \theta)\frac{s}{2\theta}$. The curvature is $\kappa = \frac{2\theta}{s}$ (equivalently, $\theta = \frac{\kappa s}{2}$), and this remains constant even as the arc is subdivided. Rewriting, $d = (1-\cos\frac{\kappa s}{2})\frac{1}{\kappa}$. From this, we can derive a precise, invertible error metric. Subdividing the arc into $n$ segments, the distance error for each segment is $\frac{1}{\kappa}(1-\cos \frac{\kappa s}{2n})$. Solving for $n$, we get:

@@

The subdivision density integral (Section~\ref{subsection:subdiv-density-int}) is fairly straightforward to compute in the forward direction, but not invertible using a straightforward closed-form equation. Numerical techniques are possible, but require multiple iterations to achieve sufficient accuracy, so are slower. In this subsection, we present a straightforward and accurate approximation, constructed piecewise from easily invertible functions. This approximation was found empirically, by interactively tuning candidate approximation functions in the Desmos graphing calculator. The exact integral and the approximation are shown in Figure~\ref{fig:espc}. Visually, it is clear that the agreement is close. We also built a test suite (included in our supplemental materials) to exhaustively test the subdivision count using a property testing approach, finding that the worst case discrepancy between approximate and exact results is 6\%. If higher flattening quality is desired at the expense of slower computation, this approximation could be used to determine a good initial value for numeric techniques; two iterations of Newton solving are enough to refine this guess to within 32-bit floating point accuracy.

The approximation is as follows:

@@

A typical pattern for converting from one curve type to another is \emph{adaptive subdivision.} An approximate curve is found in the parameter space of the target curve family. The error of the approximation is measured. If the error exceeds the specified tolerance, the curve is subdivided (typically at $t = 0.5$), otherwise the approximation is accepted. Subdivisions are also indicated at special points; for example, since quadratic Béziers cannot represent inflection points, and geometric Hermite interpolation is numerically unstable if the input curve is not convex, lowering to quadratic Béziers also requires calculation of inflection points and subdividing there. A good example of this pattern is \citet{Nehab2020}. One advantage of Euler spirals over quadratic Béziers is that they can represent inflection points just fine, so it is not necessary to solve for the inflection points, or do additional subdivision. Avoiding these alleviates the need for conditional logic and case analysis, which makes the algorithm more amenable to GPU execution.
